---
title: "Standard Statistical Hypothesis Tests in R"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: default
runtime: shiny_prerendered
description: >
  Learn about the basic syntax of R.
---


```{r setup, include=FALSE}
#devtools::install_github("rstudio/learnr")

library(learnr)
library(tidyverse)
library(janitor)
library(DT)
tutorial_options(exercise.timelimit = 10)


Pulse<-readRDS("Pulse.RDS")
SurveyData<-readRDS("SurveyData.RDS")
DemRep<-filter(SurveyData,PoliticalParty!="Independent")

selfesteem<-data.frame(ID=1:10,AttractivenessBefore=c(4,7,5,3,9,7,7,8,1,10),AttractivenessAfter=c(8,7,4,7,9,8,5,9,10,8))

```


## Quiz

### Question 1

I would like to do a t-test comparing age by political party. Summary statistics and plots are shown below.

```{r,message=FALSE}
Pulse %>%
  group_by(PoliticalParty) %>%
    summarise(mean(Age),median(Age),sd(Age),n())
```

```{r,message=FALSE}
ggplot(data=Pulse,aes(x=Age))+
  geom_histogram()+
    facet_wrap(~PoliticalParty)
```


```{r Q1, echo=FALSE}
question("Why should I not carry out a t-test on the data?",
  answer("There are not an equal number of respondents from each political party",message="Although statistical power is highest when groups are equally sized, it is never a requirement to have equal numbers of responses"),
  answer("Age is not normally distributed",message="Although age is not perfectly normally distributed, the approximation to normality looks close enough in this data"),
  answer("Political party has more than two groups",correct = TRUE,message="We can only run a t-test when we have exactly two groups. We could filter our data to remove 'independents' and then run a t-test; or look at a different statistical method"),
  answer("Respondents are not (statistically) independent of each other",message="We can assume respondents from this survey are independent (of each other)"),
  answer("Age is not coded as a numeric variable in the data",message="AgeGrp is not a numeric variable, but Age is"),
  answer("The variance of age is not equal across the groups",message="Variance is approximately equal for all groups; and this is not a requirement for the t.test funtion in R"),
  allow_retry = TRUE,random_answer_order = TRUE
)
```

### Question 2 

```{r,echo=FALSE}
Pulse %>%
  tabyl(Race,PoliticalParty)
```


```{r Q2, echo=FALSE}
question("I would like to do a chi-square comparing race by political party. A cross-tabulation is shown above. For what reason would it be innapropriate to to carry out a chi-square test on the data?",
  answer("There are not an equal number of respondents from each political party",message="Although statistical power is highest when groups are equally sized, it is never a requirement to have equal numbers of responses"),
  answer("Race is not chi-square distributed",message="This is not really a thing"),
  answer("Political party has more than two groups",message="In a Chi-square test there is no limit to the number of groups"),
  answer("Respondents are not independent of each other",message="We can assume respondents from this survey are independent"),
  answer("The expected frequencies of some combinations of the categories are very low",correct=TRUE,message="There are very low numbers of 'Asian','Latino' and 'Other' respondents which will cause problems. We could consider either filtering our data to include only 'White' and 'Black respondents; combining the 'Asian','Latino' and 'Other' categories together, or using a Fisher test"),
  allow_retry = TRUE,random_answer_order = TRUE
)
```


### Question 3


```{r,echo=FALSE}
Pulse %>%
  tabyl(Race,PoliticalParty) %>%
    adorn_percentages("row")
```

```{r Q3, echo=FALSE}
question("What code did I run to obtain the table above, showing the proportions of people supporting each political party within each race?",
         answer("Pulse %>%<br>
  tabyl(Race,PoliticalParty) %>%<br>
    adorn_percentages('row')",correct=TRUE),
   answer("Pulse %>%<br>
  tabyl(Race,PoliticalParty) %>%<br>
    adorn_percentages('col')",message="Check whether the rows sum to 1 or whether the columns sum to 1"),
   answer("Pulse %>%<br>
  tabyl(Race,PoliticalParty) %>%<br>
    adorn_pct_formatting()",message="This would add percentage formatting to a table, not calculate proportions"),
   answer("Pulse %>%<br>
  tabyl(Race,PoliticalParty) %>%<br>
    adorn_ns()", message = "This is a function. But we haven't learnt about it, so it probably isn't the right answer!")
         ,
  allow_retry = TRUE,random_answer_order = TRUE
)

```

### Question 4

I am interested in whether there was a significant difference between the average incomes by race, only considering white and black respondents. I produced some summaries, and conducted a Wilcoxon test to compare.

```{r}
Pulse %>%
  filter(Race%in%c("White","Black")) %>%
    ggplot(aes(y=Income,x=Race))+
      geom_boxplot()

Pulse %>%
  filter(Race%in%c("White","Black")) %>%
    group_by(Race)%>%
      summarise(mean(Income),median(Income))

Pulse %>%
  filter(Race%in%c("White","Black")) %>%
    wilcox.test(Income~Race,data=.)
```

```{r Q4, echo=FALSE}
question("Which of the following is an appropriate conclusion to draw from this analysis?",
         answer("There is no evidence that white and black people have different distributions of reported annual incomes",correct=TRUE),
         answer("There is strong evidence that there is no difference between distribution of reported incomes of white and black people",
                message="Hypothesis testing only ever provides evidence against the null hypothesis. It never provides evidence for the null hypothesis"),
         answer("There is some evidence to suggest that black people earn more on average than white people",
                message="Although the mean value is higher, the boxplots very clearly show that this is driven by a single observation"),
         answer("There is a probability of 0.7375 that there is no difference between the average income of white and black people",
                message="This is a common, but fundamentally incorrect, interpretation of p-values")
         ,
  allow_retry = TRUE,random_answer_order = TRUE
)

```



## 'Pulse' dataset 

The data we are using in this session is an extract of a survey conducted in the US in June 2018, as part of the Pulse of the Nation series of surveys. This survey was a representative sample of the American population. You can read more about the survey (and others from the same series) <a href="https://thepulseofthenation.com" target="_blank">here</a>. The data has been cleaned and edited slightly for use in this course.

The dataset contains an extract of 356 responses to 10 of the survey questions, and has been imported to R as a data frame called `Pulse`.

A summary of the columns in the dataset is below.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(knitr)

data.frame(Column=c("Gender","Age","AgeGrp","Race","Income","Education","PoliticalParty","PoliticalView","ApproveTrump","Attractiveness"),
           Description=c("What gender do you identify with?","What is your age?","Age range","What is your race?",
                         "About how much money do you make per year? (USD)","What is your highest level of education?",
                         "In politics today, do you consider yourself a Democrat, a Republican, or Independent?",
                         "Would you say you are liberal, conservative, or moderate?",
                         "Do you approve, disapprove, or neither approve nor disapprove of how Donald Trump is handling his job as president?",
                        "On a scale of 1-10, how physically attractive do you consider yourself?")) %>% kable()

```


```{r,echo=FALSE}
DT::datatable(Pulse)
```

(You can use the arrow keys on your keyboard to scroll right in case the data table does not fit entirely on your screen)




